Sparse Function-space Representation \\ of Neural Networks

### 2023-05-23 paper/main.tex
small thing

\section{Method details}
\label{app:method}
%
Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions. We now detail two common losses dual parameters the Gaussian (MSE) and the Bernoulli (cross entropy).  The general method is to rewrite the exponential family in the $\log$ of its natural form \ie:
\begin{equation}
 \ell(f_\weights(\mathbf{x}_{i}), y_i) = -\log p()
\end{equation}

>>>>

\section{Method details}
\label{app:method}
%
Key to our method is the ability to compute the dual parameters in \cref{eq:dual_param}. For general exponential family likelihoods we can derive simpler expressions:
\begin{equation}
 \ell(\sigma(f_{i}), y_i) = -\log p(y_i \mid f_{i}) =  A(f_i)  - y_i f_i
\end{equation}
where $A(f_i)$ is the log partition function and $\sigma(\cdots)$ is the link function. In the
